PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$

### 2014-11-24 qfenv_paper/qf_environment.tex
Chang edits
Updated figures, tables, and texts. Everything except intro!

\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$}
\author{
ChangHoon~Hahn\altaffilmark{1}, 
Michael~Blanton\altaffilmark{1}, 
John Moustakas\altaffilmark{2},
Alison~Coil\altaffilmark{3}, 
Richard~Cool\altaffilmark{4}, 
Daniel Eisenstein\altaffilmark{5},
Ken Wong\altaffilmark{6}, 
Guangtun Zhu\altaffilmark{7}
}
\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003}
\altaffiltext{2}{Department of Physics and Astronomy, Siena College, 515 Loudon Road, Loudonville, NY 12211}
\altaffiltext{3}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, 9500 Gilman Dr., La Jolla, CA 92093}
\altaffiltext{4}{MMT Observatory, University of Arizona, 1540 E Second Street, Tucson AZ 85721}
\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{6}{Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson, AZ 85721} 
\altaffiltext{7}{Department of Physics and Astronomy, The Johns Hopkins University, 3400 North Charles Street, Baltimore, MD 21218} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We investigate the effects of galaxy environment on the evolution of
the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using
spectroscopic redshifts and multi-wavelength imaging data from the
PRIsm MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey
(SDSS). Our stellar mass limited galaxy sample consists of $\sim
13,000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 64,000$ SDSS
galaxies within $z = 0.05-0.12$. We classify the galaxies as quiescent
or star-forming based on an evolving specific star formation cut, and
as low or high density environments based on fixed cylindrical
aperture environment measurements on a volume-limited environment
defining population. For quiescent and
star-forming galaxies in low or high density environments, we examine
the evolution of their stellar mass function (SMF). Then using the
SMFs we compute $f_{\rm{Q}}(\mathcal{M}_{*})$ and quantify its
evolution within our redshift range. We find that the quiescent
fraction is higher at higher masses and in denser environments. The
quiescent fraction rises with cosmic time for all masses and
environments. At a fiducial mass of $10^{10.5}M_\odot$, from $z\sim
0.7$ to $0.1$, the quiescent fraction rises by $15\%$ at the
lowest environments and by $25\%$ at the highest environments we measure.
These results suggest that for a minority of galaxies their cessation
of star formation is due to external influences on
them. However, in the recent Universe a substantial fraction of the
galaxies that cease forming stars do so due to internal processes.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GALAXY SAMPLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*} 
  \caption{Galaxy Subsamples}
  \label{tab:subsample}
  \begin{center}
    \leavevmode
    \begin{tabular}{ccccccc} \hline \hline              
     &\multicolumn{1}{c}{$n_{\rm{env}}$}        & \multicolumn{2}{c}{$N_{\rm{gal}}$}  & \multicolumn{2}{c}{$\mathcal{M}_{\rm{lim}}$} & $M_{\rm{r}, lim}$ \\ 
    & & Quiescent & Star-Forming & Quiescent & Star-Forming &  \\ \hline 
$0.05 < z < 0.12$ & $n_{\rm{env}} < \lowenvthresh $ & 4969 & 5943 & $10^{10.2} \mathcal{M}_{\odot}$ & $10^{10.2} \mathcal{M}_{\odot}$ & -20.98 \\
               & $n_{\rm{env}} > \highenvthresh $ &17488 & 12244 &                          \\ 
                              & all          &$33968$                       & $30058$                          \\ \hline
$0.2 < z < 0.4$      &$n_{\rm{env}} < \lowenvthresh $           &282                    &1020 & $10^{9.8} \mathcal{M}_{\odot}$ & $10^{9.8} \mathcal{M}_{\odot}$ &-21.10 \\
               &$n_{\rm{env}} > \highenvthresh $            &410                    &850                           \\
               & all                & $995$                      & $2628$                          \\ \hline
$0.4 < z < 0.6$      &$n_{\rm{env}} < \lowenvthresh $           &426                       &1226 & $10^{10.3} \mathcal{M}_{\odot}$ & $10^{10.3} \mathcal{M}_{\odot}$ & -21.06 \\
               &$n_{\rm{env}} > \highenvthresh $            &543                       &983                           \\
               & all               & $1462$                      & $3334$                          \\ \hline
$0.6 < z < 0.8$      &$n_{\rm{env}} < \lowenvthresh $           &389                       &932  & $10^{10.7} \mathcal{M}_{\odot}$ & $10^{10.6} \mathcal{M}_{\odot}$ & -20.90 \\
               &$n_{\rm{env}} > \highenvthresh $            &642                       &907                           \\
               & all              & $1590$                      & $2852$                          \\ \hline
Total &      & \multicolumn{2}{c}{76887} & \\ \hline
  \multicolumn{4}{l}{}                                             \\       
    \end{tabular} \par
    \end{center}
%    \bigskip 
    {\bf Notes}: Number of galaxies ($N_{\rm{gal}}$) in the mass complete subsamples within the edges of the survey (Section \ref{sec:sample}). The subsamples are classified based on environment $n_{\rm{env}}$ and star formation rate (star-forming or quiescent). The lowest redshift bin is derived from SDSS; the rest are from PRIMUS. We also list the stellar mass completeness limit $\mathcal{M}_{\rm{lim}}$ for our sample and the $r$-band absolute magnitude limits $M_{\rm{r}, lim}$ for the Environment Defining Population. 
    \bigskip
\end{table*}

@@

Since we are ultimately interested in a mass complete galaxy sample to
derive SMFs and QFs, next we impose stellar mass completeness limits
to our galaxy sample.
Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS are functions of redshift, the apparent magnitude limit of the survey, and the typical stellar mass-to-light ratio of galaxies near the flux limit. We use the same procedure as \cite{Moustakas:2013aa}, which follows \cite{Pozzetti:2010aa}, to empircally determine the stellar mass completeness limits. For each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\log \; \mathcal{M}_{\mathrm{lim}} = \log \; \mathcal{M} + 0.4 (m - m_{\mathrm{lim}})$, where $\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was equal to the survey magnitude limit, $m$ is the observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields. We construct a cumulative distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ faintest galaxies in $\Delta z=0.04$ bins. In each of these redshift bins, we calculate the minimum stellar mass that includes $95 \%$ of the galaxies. Separately for quiescent and star-forming galaxies, we fit quadratic polynomials to the minimum stellar masses versus redshift (star-forming or quiescent classification is described in the following section). Finally, we use the polynomials to obtain the minimum stellar masses at the center of redshift bins, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$, which are then used as PRIMUS stellar mass completeness limits.

@@

We now have a stellar mass complete sample derived from SDSS-{\em
  GALEX} and PRIMUS data. Since our sample is derived from two
different surveys, we account for the disparity in the redshift
uncertainty. While PRIMUS provides a large number of redshifts out to
$z = 1$, due to its use of a low dispersion prism, the redshift
uncertainties are significantly larger ($\sigma_{z}/(1+z) \approx 0.5
\%$) than that of the SDSS-{\em GALEX} redshifts. In order to have
comparable environment measures throughout our redshift range, we
apply PRIMUS redshift uncertainties to our galaxy sample selected from
SDSS-{\em GALEX}. For each SDSS-{\em GALEX} galaxy, we adjust its
redshift by randomly sampling a Gaussian distribution with standard
deviation $\sigma = 0.005 (1+z_{\rm{SDSS}-GALEX})$, where
$z_{\rm{SDSS}-GALEX}$ is the redshift of the galaxy.

@@

    \caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample within the edges. A fixed cylindrical aperture of $R_{\rm{ap}} =\apradius\;\rm{Mpc}$ and $H_{\rm{ap}} = \apheight\; \rm{Mpc}$ is used to measure environment. The star-forming galaxies contribution to the distribution is colored blue and diagonally patterned. The contribution from quiescent galaxies is colored in red. For each redshift panel, galaxies with $n_{\mathrm{env}} < 0.5$ are in low density environments and galaxies with $n_{\rm{env}} > 3.0$ are in high density environment. We note that the significant difference among the SDSS distribution and the PRIMUS distributions above is due to the different stellar mass completeness limits imposed on each redshift bin of our galaxy sample.}      \label{fig:envcount}

@@

In constructing the PRIMUS EDP we use the same PRIMUS data used to select our galaxy sample (described in Section \ref{sec:target}). We again restrict the PRIMUS galaxies to $0.2 < z < 0.8$ and divide them into bins of $\Delta z = 0.2$. Before we consider the cumulative number densities in the redshift bins, we first determine the $M_r$ limit for the highest redshift bin ($0.6-0.8$) by examining the $M_{r}$ distribution with bin size $\Delta M_{r} = 0.25$ and select $M_{r,\rm{lim}}$ near the peak of the distribution where bins with $M_{r} > M_{r,\rm{lim}}$ have fewer galaxies than the bin at $M_{r, \rm{lim}}$. We conservatively choose $M_{r, \rm{lim}}(0.6 < z < 0.8)$ to be $M_{r} = -21.0$. Then for the lower redshift bins, we impose absolute magnitude limits ($M_{r,\rm{lim}}$) such that the cumulative number density, calculated with the galaxy statistical weights, of the bin ordered by $M_{r}$ is equal to the cumulative number density of the highest redshift bin at $M_{r, \rm{lim}}(0.6 < z < 0.8) = -20.97$.

For the SDSS EDP, we do not use the SDSS-{\em GALEX} parent data,
which is limited to the combined angular selection window of the
VAGC and {\em GALEX} (Section \ref{sec:sdss}). Instead, since FUV, NUV
values are not necessary for the EDP, we extend the parent data of the
SDSS EDP to the entire NYU VAGC, including galaxies outside of the
{\em GALEX} window function. Furthermore, we impose a redshift range
of $0.05-0.12$ on the SDSS EDP. This redshift range was determined to
account for the lack of faint galaxies at $z \sim 0.2$ and the lack of
bright galaxies at $z \sim 0.01$ in the VAGC. As with the PRIMUS
redshift bins, we determine the SDSS EDP $M_{r, \rm{lim}}$ by matching
the cumulative number density of the highest redshift bin. For
redshift bins $z = 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$ we get
$M_{r,\rm{lim}} = -20.95$, $-21.03$, $-20.98$ and $-20.97$,
respectively. These absolute magnitude limits are illustrated in
Figure \ref{fig:targetEDP}, where we present the absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) ad the EDP (red circles). 
The left-most panel corresponds to the sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$. 
Figure \ref{fig:targetEDP} shows clear $M_r$ cutoffs in the
$M_{r}$ distribution versus redshift for the EDP on top
of the target galaxy sample.

@@

Finally, we measure the environment for each galaxy in our galaxy
sample by counting the number of EDP galaxies, $n_{\rm{env}}$ with RA,
Dec, and $z$ within our cylindrical aperture centered around
it. $n_{\rm{env}}$ accounts for the statistical weights of the EDP
galaxies. 
For our galaxy sample, the expected $n_{\rm{env}}$ given the constant number density in 
each of our EDP redshift bin and volume of our cylindrical aperture is $< n_{\rm{env}} > = 1.3$. 
Once we obtain environment measurements for all the galaxies
in our galaxy sample, we classify galaxies with $n_{\rm{env}} < 0.5$
to be ``low" environment density and galaxies with $n_{\rm{env}} > 3$
to be ``high" environment densities. The high environment cutoff was
selected in order to reduce contamination from galaxies in low
environment densities while maintaining sufficient statistics. In
Section \ref{sec:env_qf_evol} we will also explore higher density
cutoffs for $n_{\rm{env}}$.

The analysis we describe below uses a fixed cylindrical aperture with
dimensions $R_{\rm{ap}} = \apradius \; \rm{Mpc}$ and $H_{\rm{ap}} = \apheight
\;\rm{Mpc}$ to measure environment. The same analysis was
extended for varying aperture dimensions $R_{\rm{ap}} = 1.5, \apradius, 3.0 \:
\rm{Mpc}$ and $H_{\rm{ap}} = \apheight, 70 \;\rm{Mpc}$. We also
adjusted the environment classification thresholds for these
analyses. The results obtained from using different apertures and
environment classification thresholds are qualitatively consistent with the results presented below.

@@

To account for these edge effects, we use a Monte Carlo method to impose edge cutoffs on our galaxy sample. First, using \texttt{ransack} from \cite{Swanson:2008aa}, we construct a random sample of  $N_{\rm{ransack}} = 1,000,000$ points with RA and Dec randomly selected within the window function of the EDP (SDSS EDP and PRIMUS EDP separately). We then compute the angular separation, $\theta_{i, \rm{ap}}$ that corresponds to $R_{\rm{ap}}$ (Section \ref{sec:environment}) at the redshift of each sample galaxy $i$. For each sample galaxy we count the number of \texttt{ransack} points within $\theta_{i, \rm{ap}}$ of the galaxy: $n_{i,\rm{ransack}}$. Afterwards, we compare $n_{i,\rm{ransack}}$ to the expected value computed from the angular area of the environment defining aperture and the EDP window function: 
\begin{equation} \label{eq:ransack}
\langle n_{\rm{ransack}}\rangle_{i} = \frac{N_{\rm{ransack}}}{A_{\rm{EDP}}}\times {\pi \theta_{i, \rm{ap}}^2} \times f_{\rm{thresh}}. 
\end{equation} 
$A_{\rm{EDP}}$ is the total angular area of the EDP window function and $f_{\rm{thresh}}$ is the fractional threshold for the edge effect cut-off. For $R_{\rm{ap}}= \apradius \;\rm{Mpc}$, $f_{\rm{thresh}} = 0.75$. If $n_{i, \rm{ransack}}$ is greater than $<n_{\rm{ransack}}>_i$ then galaxy $i$ remains in our sample; otherwise, it is discarded.

Once the edge effect cuts are applied, we are left with the final galaxy sample. In Figure \ref{fig:envcount} we present the distribution of environment measurements ($n_{\rm{env}}$) for our final galaxy sample in redshift bins: $0.05 - 0.12$, $0.2 - 0.4$, $0.4-0.6$, and $0.6-0.8$. The quiescent galaxy contributions are colored in red while the star-forming galaxy contributions are colored in blue and patterned. The low and high density environment classifications are represented by black vertical lines that divide the distribution at $n_{\rm{env}} = 0.5$ and $n_{\rm{env}} = 3.5$. The percentage of the total galaxies in the redshift bin that are in these environment densities are labeled on the figure.

>>>>

\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$}
\author{
ChangHoon~Hahn\altaffilmark{1}, 
Michael R.~Blanton\altaffilmark{1}, 
John~Moustakas\altaffilmark{2},
Alison L.~Coil\altaffilmark{3}, 
Richard J.~Cool\altaffilmark{4}, 
Daniel J.~Eisenstein\altaffilmark{5},
Kenneth C.~Wong\altaffilmark{6}, 
Guangtun~Zhu\altaffilmark{7}
}
\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003}
\altaffiltext{2}{Department of Physics and Astronomy, Siena College, 515 Loudon Road, Loudonville, NY 12211}
\altaffiltext{3}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, 9500 Gilman Dr., La Jolla, CA 92093}
\altaffiltext{4}{MMT Observatory, University of Arizona, 1540 E Second Street, Tucson AZ 85721}
\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{6}{Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson, AZ 85721} 
\altaffiltext{7}{Department of Physics and Astronomy, The Johns Hopkins University, 3400 North Charles Street, Baltimore, MD 21218} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We investigate the effects of galaxy environment on the evolution of
the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using
spectroscopic redshifts and multi-wavelength imaging data from the
PRIsm MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey
(SDSS). Our stellar mass limited galaxy sample consists of $\sim
13,000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 64,000$ SDSS
galaxies within $z = 0.05-0.12$. We classify the galaxies as quiescent
or star-forming based on an evolving specific star formation cut, and
as low or high density environments based on fixed cylindrical
aperture environment measurements on a volume-limited environment
defining population. For quiescent and
star-forming galaxies in low or high density environments, we examine
the evolution of their stellar mass function (SMF). Then using the
SMFs we compute $f_{\rm{Q}}(\mathcal{M}_{*})$ and quantify its
evolution within our redshift range. We find that the quiescent
fraction is higher at higher masses and in denser environments. The
quiescent fraction rises with cosmic time for all masses and
environments. At a fiducial mass of $10^{10.5}M_\odot$, from $z\sim
0.7$ to $0.1$, the quiescent fraction rises by $15\%$ at the
lowest environments and by $25\%$ at the highest environments we measure.
These results suggest that for a minority of galaxies their cessation
of star formation is due to external influences on
them. However, in the recent Universe a substantial fraction of the
galaxies that cease forming stars do so due to internal processes.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GALAXY SAMPLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*} 
  \caption{Galaxy Subsamples}
  \label{tab:subsample}
  \begin{center}
    \leavevmode
    \begin{tabular}{ccccccc} \hline \hline              
     &\multicolumn{1}{c}{$n_{\rm{env}}$}        & \multicolumn{2}{c}{$N_{\rm{gal}}$}  & \multicolumn{2}{c}{$\mathcal{M}_{\rm{lim}}$} & $M_{\rm{r}, lim}$ \\ 
    & & Quiescent & Star-Forming & Quiescent & Star-Forming &  \\ \hline 
$0.05 < z < 0.12$ & $n_{\rm{env}} < \lowenvthresh $ & 6533 & 7508 & $10^{10.2} \mathcal{M}_{\odot}$ & $10^{10.2} \mathcal{M}_{\odot}$ & -20.95 \\
               & $n_{\rm{env}} > \highenvthresh $ &14673 & 9717 &                          \\ 
                              & all          &$33553$                       & $29864$                          \\ \hline
$0.2 < z < 0.4$      &$n_{\rm{env}} < \lowenvthresh $           &363                    &1231 & $10^{9.8} \mathcal{M}_{\odot}$ & $10^{9.8} \mathcal{M}_{\odot}$ &-21.03 \\
               &$n_{\rm{env}} > \highenvthresh $            &379                    &756                           \\
               & all                & $1086$                      & $2879$                          \\ \hline
$0.4 < z < 0.6$      &$n_{\rm{env}} < \lowenvthresh $           &536                       &1498 & $10^{10.3} \mathcal{M}_{\odot}$ & $10^{10.3} \mathcal{M}_{\odot}$ & -20.98 \\
               &$n_{\rm{env}} > \highenvthresh $            &490                       &854                           \\
               & all               & $1560$                      & $3577$                          \\ \hline
$0.6 < z < 0.8$      &$n_{\rm{env}} < \lowenvthresh $           &567                       &1254  & $10^{10.7} \mathcal{M}_{\odot}$ & $10^{10.6} \mathcal{M}_{\odot}$ & -20.97 \\
               &$n_{\rm{env}} > \highenvthresh $            &498                       &671                           \\
               & all              & $1668$                      & $2964$                          \\ \hline
Total &      & \multicolumn{2}{c}{77151} & \\ \hline
  \multicolumn{4}{l}{}                                             \\       
    \end{tabular} \par
    \end{center}
%    \bigskip 
    {\bf Notes}: Number of galaxies ($N_{\rm{gal}}$) in the mass complete subsamples within the edges of the survey (Section \ref{sec:sample}). The subsamples are classified based on environment ($n_{\rm{env}}$) and star formation rate (star-forming or quiescent). The lowest redshift bin is derived from SDSS; the rest are from PRIMUS. We also list the stellar mass completeness limit, $\mathcal{M}_{\rm{lim}}$, for our sample along with the $r$-band absolute magnitude limits, $M_{\rm{r}, lim}$, for the Environment Defining Population. 
    \bigskip
\end{table*}

@@

Since we are ultimately interested in a mass complete galaxy sample to
derive SMFs and QFs, next we impose stellar mass completeness limits
to our galaxy sample.
Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS are functions of redshift, the apparent magnitude limit of the survey, and the typical stellar mass-to-light ratio of galaxies near the flux limit. We use the same procedure as \cite{Moustakas:2013aa}, which follows \cite{Pozzetti:2010aa}, to empircally determine the stellar mass completeness limits. For each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\log \; \mathcal{M}_{\mathrm{lim}} = \log \; \mathcal{M} + 0.4\;(m - m_{\mathrm{lim}})$, where $\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was equal to the survey magnitude limit, $m$ is the observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields. We construct a cumulative distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ faintest galaxies in $\Delta z=0.04$ bins. In each of these redshift bins, we calculate the minimum stellar mass that includes $95 \%$ of the galaxies. Separately for quiescent and star-forming galaxies, we fit quadratic polynomials to the minimum stellar masses versus redshift (star-forming or quiescent classification is described in the following section). Finally, we use the polynomials to obtain the minimum stellar masses at the center of redshift bins, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$, which are then used as PRIMUS stellar mass completeness limits.

@@

We now have a stellar mass complete sample derived from SDSS-{\em
  GALEX} and PRIMUS data. Since our sample is derived from two
different surveys, we account for the disparity in the redshift
uncertainty. While PRIMUS provides a large number of redshifts out to
$z = 1$, due to its use of a low dispersion prism, the redshift
uncertainties are significantly larger ($\sigma_{z}/(1+z) \approx 0.5
\%$) than that of the SDSS-{\em GALEX} redshifts. In order to have
comparable environment measures throughout our redshift range, we
apply PRIMUS redshift uncertainties to our galaxy sample selected from
SDSS-{\em GALEX}. For each SDSS-{\em GALEX} galaxy, we adjust its
redshift by randomly sampling a Gaussian distribution with standard
deviation $\sigma = 0.005 (1+z_{\mathrm{SDSS}-GALEX})$, where
$z_{\mathrm{SDSS}-GALEX}$ is the redshift of the galaxy.

@@

    \caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample within the survey edges. A fixed cylindrical aperture of $R_{\rm{ap}} =\apradius\;\rm{Mpc}$ and $H_{\rm{ap}} = \apheight\; \rm{Mpc}$ is used to measure environment. The star-forming galaxies contribution to the distribution is colored in blue and diagonally patterned. The contribution from quiescent galaxies is colored in red. Galaxies with $n_{\mathrm{env}} < 0.5$ are in low density environments and galaxies with $n_{\rm{env}} > 3.0$ are in high density environment. We note that the significant difference among the SDSS distribution and the PRIMUS distributions above is due to the different stellar mass completeness limits imposed on each redshift bin of our galaxy sample.}      \label{fig:envcount}

@@

In constructing the PRIMUS EDP we use the same PRIMUS data used to select our galaxy sample (described in Section \ref{sec:target}). We again restrict the PRIMUS galaxies to $0.2 < z < 0.8$ and divide them into bins of $\Delta z = 0.2$. Before we consider the cumulative number densities in the redshift bins, we first determine the $M_r$ limit for the highest redshift bin ($z = 0.6-0.8$) by examining the $M_{r}$ distribution with bin size $\Delta M_{r} = 0.25$ and select $M_{r,\rm{lim}}$ near the peak of the distribution where bins with $M_{r} > M_{r,\rm{lim}}$ have fewer galaxies than the bin at $M_{r, \rm{lim}}$. We conservatively choose $M_{r, \rm{lim}}(0.6 < z < 0.8)$ to be $M_{r} = -20.97$. Then for the lower redshift bins, we impose absolute magnitude limits ($M_{r,\rm{lim}}$) such that the cumulative number density, calculated with the galaxy statistical weights, of the bin ordered by $M_{r}$ is equal to the cumulative number density of the highest redshift bin with $M_{r, \rm{lim}}(0.6 < z < 0.8) = -20.97$.

For the SDSS EDP, we do not use the SDSS-{\em GALEX} parent data,
which is limited to the combined angular selection window of the
VAGC and {\em GALEX} (Section \ref{sec:sdss}). Instead, since FUV, NUV
values are not necessary for the EDP, we extend the parent data of the
SDSS EDP to the entire NYU-VAGC, including galaxies outside of the
{\em GALEX} window function. Furthermore, we impose a redshift range
of $0.05-0.12$ on the SDSS EDP. This redshift range was determined to
account for the lack of faint galaxies at $z \sim 0.2$ and the lack of
bright galaxies at $z \sim 0.01$ in the VAGC. As with the PRIMUS
redshift bins, we determine the SDSS EDP $M_{r, \rm{lim}}$ by matching
the cumulative number density of the highest redshift bin. For
redshift bins $z = 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$ we get
$M_{r,\rm{lim}} = -20.95$, $-21.03$, $-20.98$ and $-20.97$,
respectively. These absolute magnitude limits are illustrated in
Figure \ref{fig:targetEDP}, where we present the absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) ad the EDP (red circles). 
The left-most panel corresponds to the sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$. 
Figure \ref{fig:targetEDP} shows clear $M_r$ cutoffs in the
$M_{r}$ distribution versus redshift for the EDP on top
of our galaxy sample.

@@

Finally, we measure the environment for each galaxy in our galaxy
sample by counting the number of EDP galaxies, $n_{\rm{env}}$, with RA,
Dec, and $z$ within our cylindrical aperture centered around
it. $n_{\rm{env}}$ accounts for the statistical weights of the EDP
galaxies. 
For our galaxy sample, the expected $n_{\rm{env}}$ given the uniform number density in 
each of our EDP redshift bin and volume of our cylindrical aperture is $\langle n_{\rm{env}} \rangle = 1.3$. 
Once we obtain environment measurements for all the galaxies
in our galaxy sample, we classify galaxies with $n_{\rm{env}} < 0.5$
to be in ``low" environment densities and galaxies with $n_{\rm{env}} > 3$
to be in ``high" environment densities. The high environment cutoff was
selected in order to reduce contamination from galaxies in low
environment densities while maintaining sufficient statistics. In
Section \ref{sec:env_qf_evol} we will also explore higher density
cutoffs for $n_{\rm{env}}$.

The analysis we describe below uses a fixed cylindrical aperture with
dimensions $R_{\rm{ap}} = \apradius \; \rm{Mpc}$ and $H_{\rm{ap}} = \apheight
\;\rm{Mpc}$ to measure environment. The same analysis was
extended for varying aperture dimensions $R_{\rm{ap}} = 1.5, \: \apradius, \:3.0 \:
\rm{Mpc}$ and $H_{\rm{ap}} = \apheight, \; 70 \;\rm{Mpc}$ with adjusted environment classifications. 
The results obtained from using different apertures and
environment classifications are qualitatively consistent with the results presented below.

@@

To account for these edge effects, we use a Monte Carlo method to impose edge cutoffs on our galaxy sample. First, using \texttt{ransack} from \cite{Swanson:2008aa}, we construct a random sample of  $N_{\rm{ransack}} = 1,000,000$ points with RA and Dec randomly selected within the window function of the EDP (SDSS EDP and PRIMUS EDP separately). We then compute the angular separation, $\theta_{i, \rm{ap}}$ that corresponds to $R_{\rm{ap}}$ (Section \ref{sec:environment}) at the redshift of each sample galaxy $i$. For each sample galaxy we count the number of \texttt{ransack} points within $\theta_{i, \rm{ap}}$ of the galaxy: $n_{i,\rm{ransack}}$. Afterwards, we compare $n_{i,\rm{ransack}}$ to the expected value computed from the angular area of the environment defining aperture and the EDP window function: 
\begin{equation} \label{eq:ransack}
\langle n_{\rm{ransack}}\rangle_{i} = \frac{N_{\rm{ransack}}}{A_{\rm{EDP}}}\times {\pi \theta_{i, \rm{ap}}^2} \times f_{\rm{thresh}}. 
\end{equation} 
$A_{\rm{EDP}}$ is the total angular area of the EDP window function and $f_{\rm{thresh}}$ is the fractional threshold for the edge effect cut-off. For $R_{\rm{ap}}= \apradius \;\rm{Mpc}$, $f_{\rm{thresh}} = 0.75$. If $n_{i, \rm{ransack}} > \langle n_{\rm{ransack}} \rangle_i$ then galaxy $i$ remains in our sample; otherwise, it is discarded. Once the edge effect cuts are applied, we are left with the final galaxy sample. For our SDSS-{\em GALEX} galaxy sample, $\sim 12 \%$ of galaxies are removed from the edge effect cuts. For our PRIMUS galaxy sample, $\sim 40 \%$ of galaxies are removed from the edge effect cuts.

In Figure \ref{fig:envcount} we present the distribution of environment measurements ($n_{\rm{env}}$) for our final galaxy sample in redshift bins: $z = 0.05 - 0.12$, $0.2 - 0.4$, $0.4-0.6$, and $0.6-0.8$. The quiescent galaxy contributions are colored in red while the star-forming galaxy contributions are colored in blue and patterned. We classify galaxies with $n_{\mathrm{env}} < 0.5$ to be in low density environments and galaxies with $n_{\mathrm{env}} > 3.0$ to be in high density environments.
